Modelling the gas kinematics of an atypical Lyman alpha emitting compact dwarf galaxy

### 2017-06-29 paper/paper.tex
full revision complete

\begin{table}
\begin{center}
\begin{tabular}{lc}\hline
$\alpha$(2000)$^{a}$ & 12h17min17.1s\\
$\delta$(2000)$^{b}$ & -28d02m32s\\
$l$, $b$ (deg) & 294, 34\\
$m_V$ & 17.5\\
  M$_V$ & -17.6\\ 
$z$ & $0.0259\pm0.0002$ \\\hline
\end{tabular}
\end{center}
\caption{Basic observational characteristics of \tol\ 
  \citep{Thuan97}\label{obstable}} 
\end{table}

\begin{table*}
  \centering
\begin{tabular}{l|lrrr}
\hline
  Parameter  & Description & Fiducial value & Allowed range & Units \\ \hline\hline
$v_{\infty,\,{\rm cl}}$ & Radial cloud velocity & $100.0$ & [$0.0$, $800.0$] & $\,{\rm km\,s}^{-1}$ \\
$\sigma_{\rm {\rm cl}}$ & Random cloud motion &$40.0$ & [$5.0$, $100.0$] & $\,{\rm km\,s}^{-1}$ \\
$P_{\rm {\rm cl}}$ & Probability to be emitted in cloud & $0.35$ & [$0.0$, $1.0$] &  \\
$r_{\rm {\rm cl}}$ & Cloud radius & $100.0$ & [$30.0$, $200.0$] & $\,{\rm pc}$ \\
$H_{\rm em}$ & Emission scale radius & $1000.0$ & [$500.0$, $3.0\times 10^{3}$] & $\,{\rm pc}$ \\
$f_{\rm {\rm cl}}$ & Cloud covering factor & $3.5$ & [$0.8$, $8.0$] &  \\
$T_{\rm {\rm ICM}}$${}^{\dagger}$ & Temperature of ICM & $10^{6}$ & [$3.0\times 10^{5}$, $5.0\times 10^{7}$] & $\,{\rm K}$ \\
$n_{\rm HI,\,{\rm ICM}}$${}^{\dagger}$ & \HI number density in ICM & $5.0\times 10^{-8}$ & [$10^{-12}$, $10^{-6}$] & $\,{\rm cm}^{-3}$ \\
$\sigma_{\rm i}$ & Width of emission profile & $50.0$ & [$5.0$, $100.0$] & $\,{\rm km\,s}^{-1}$ \\
$T_{\rm {\rm cl}}$${}^{\dagger}$ & Temperature in clouds & $10^{4}$ & [$5.0\times 10^{3}$, $5.0\times 10^{4}$] & $\,{\rm K}$ \\
$\beta_{\rm cl}$ & Steepness of the radial velocity profile & $1.5$ & [$1.1$, $2.5$] &  \\
$\tilde\sigma_{\rm d, cl}$${}^{\dagger}$ & Dust content in clumps & $3.2\times10^{-22}$ & [$4.7\times 10^{-24}$, $1.6\times 10^{-21}$] & $\,\cm^{2}$ \\
$\zeta_d$${}^{\dagger}$ & Ratio of ICM to cloud dust abundance & $0.01$ & [$10^{-4}$, $0.1$] &  \\
$n_{\rm HI,\,{\rm cl}}$${}^{\dagger}$ & \HI number density in clouds & $0.35$ & [$0.03$, $3.0$] & $\,{\rm cm}^{-3}$ \\
\hline
\end{tabular}
  \caption{Overview of the parameters in the multiphase model and its fiducial
    values. Variables marked with ${}^{\dagger}$ were drawn in
    log-space. Details of the implementation are in \citet{Gronke2016}.}
  \label{tab:models}
\end{table*}

@@

The idealized multiphase model consists of spherical, cold, dense
clumps of neutral hydrogen (and dust) embedded in a hot, ionized
medium \citep{Gronke2016}. 
The clumps also have a random and an outflowing velocity
component which totals the number of parameters describing the model
to be $14$, which also include information about the spatial
distribution and thermal state of the clumps and the intraclump
medium. 
We do not explore inflowing clumps given the slight line asymmetry
redwards to the line center (see the dots in Figure \ref{fig:results})

@@

We compare each resulting spectra to the observational results from
\tol\ after normalizing the observed and simulated spectra to have a 
flux integral of one.
We build a $\chi^2$ on the normalized flux measurements for each one
of the $2500$ models

\begin{equation}
\chi^2 = \sum_{i} \frac{({f}_i - \hat{f}_i)^2}{\sigma_i^2}, 
\label{eq:chi2}
\end{equation}
%
where $i$ iterates over velocity bins, $f_{i}$ is the observed flux,
$\sigma_i$ is the observed flux uncertainty and $\hat{f}_i$ is the
model estimated flux.
We do not have analytic expression for $\hat{f}$, instead we use the
results of the MonteCarlo to build histograms that play the role of
$\hat{f}$.

We select for further analysis the best $1\%$ models according to the
lowest $\chi^2$ values.
We note that the difference between the lowest and highest $\chi^2$ values in
those $25$ models is close to $\Delta\chi^2 = 3000$, the lowest
$\chi^2$ being close to $\chi^2_{min}=1200$. 
The total number of degrees of freedom, $d.o.f$, is $104$.

We divide the results in two classes: low $\chi^2/d.o.f.<35$ and high
$\chi^2/d.o.f.35>$.
We apply a random forest classification algorithm to find the
more relevant parameters in splitting the results into these two
classes. 
The algorithm uses $500$ trees for the classification and a
maximum of $3$ depth levels. 
To check for tability we repeat the computation $10$ times by
randomly subsampling the input data to use $80\%$ of the data as a
training set.

@@

We use an analytical approximation that captures the most important
effects of rotation onto the \lya\ line. 
We defer the reader to \citet{GaravitoCamargo2014} for complete
details on the explicit form of this approximation.
To fully explore the
parameter space using a Markov Chain Monte Carlo (MCMC) calculation with the
\texttt{emcee} Python library \citep{2013PASP..125..306F}. \texttt{emcee} 
is an open source optimized implementation of the affine-invariant 
MCMC sampler \citep{goodman2010ensemble}. 
The algorithm creates a number of walkers that,
during a sufficient number of steps, generate parameters' combinations
for a specific model.
For each timestep, the code calculates the likelihood of the
combination with respect to the observational data.
The walkers explore the parameter space sampling the Gaussian likelihood
function built as $\propto \exp(-\chi^2/2)$, where the $\chi^2$ follows
the definition in Equation \ref{eq:chi2}. 
We do not have an analytic expresion for $\hat{f}$, we compute it
by numerical integration of the analytical approximations found in
\citet{GaravitoCamargo2014}.

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.95\textwidth]{tree_result.pdf}
\caption{Classification tree example. 
The aim is to find the parameters that separate two
classes: low $\chi^2/d.o.f. < 35$ and high $\chi^2/d.o.f>35$. 
Each box describes the condition over the parameter of interest, the
level of sample impurity, the number of samples and the value of the
number of samples in each classes.  
In this example we randomly sample $80\%$ of the full set of models to
start with $28$ models in the first class and
$1962$ models in the second class; the best way to increase the
probability to find a  a result with low $\chi^2/d.o.f.$ ($13$ models) is having $v_{\infty,{\rm cl}}<157.0$ \kms,
$\sigma_{{\rm cl}}>55.6$ \kms and $P_{\rm cl}>0.683$.
The final classification is not perfect, showing that all other
parameters are also important but these three are the most relevant.  
\label{fig:tree}}
\end{center}
\end{figure*}

\begin{figure*}
\begin{center}
  \includegraphics[width=0.6\textwidth]{vinf_cl.pdf}
  \includegraphics[width=0.6\textwidth]{P_cl.pdf}
  \includegraphics[width=0.6\textwidth]{sigma_cl.pdf}
\caption{Results from the multiphase  model.
  We only show results for the three parameters with a significant
  statistical difference between the models with the lowest $\chi^2$
  values and its prior distribution. 
  These three parameters are the clump radial velocity at infinity 
  $v_{\infty, \rm{cl}}$; the probability that  the \lya\ photons were
  emitted in the clumps, $P_{\rm cl}$; the clump velocity dispersion,
  $\sigma_{\rm cl}$.
  The left column corresponds to the parameter's integrated distributions for
  models with the lowest $\chi^2$ values (dotted line) compared against the
  parameter's prior integrated distributions (continuous line).
  The right column shows a scatter plot of $\chi^2$ (normalized by the
  degrees of freedom) and its corresponding physical parameters.
  The clump kinematic state is the key ingredient to
  reproduce \tol's \lya\ line morphology.
  \label{multiphaseresults}
}  
\end{center}
\end{figure*}

@@

Figure \ref{fig:tree} shows as an illustration the results for a
classification tree.  
The tree starts with $28$ and $1962$ models in the low and high
$\chi^2/d.o.f.$ classes, respectively. 
We find that the best classification
yields $13$ and $44$ models in the low and high $\chi^2\d.o.f.$
classes, respectively, after selecting for $v_{\infty,{\rm cl}}<157.0$ \kms,
$\sigma_{{\rm cl}}>55.6$ \kms and $P_{\rm cl}>0.683$. 
The split in two classes is not perfect. 
This means that the 3 parameters in the
model are the most influential in finding models with low
$\chi^2/d.o.f.$, but that some combinations of the other 11 parameters
are also relevant to find a good fit.

@@

The best models are summarized in Figure \ref{multiphaseresults}.
Left column show the difference between the integrated distributions
of the full sample (2500 input models) and the models with the lowest
$\chi^2/d.o.f.$. 
The right column shows the actual $\chi^2/d.o.f.$ 
and its corresponding parameter value. 
Under these conditions we find $\sigma_{\rm cl}=$\sigmaclump,
$v_{\infty {\rm, cl}}=$\inftyclump\ and $P_{\rm cl}=$\probaclump.

@@

Having constrained only 3 parameters, one migh wonder why the other 11
parameters do not seem to matter. 
However, this view is misleading. 
Even if for clumply models the line profile is most sensitive to only
a few parameters \citep{Gronke2016}, there are the rest of parameters
which affect the line profile at a level that cannot be neglected,
i.e. we cannot randomly pick 11 random, reasonable values for these
parameters, and expect to fit the line profile while only varying the
other 3, as the results for the classification tree example show in
Figure \ref{fig:tree}.

We cannot discard that another region of parameter space
could also work.
It might be interesting to explore in the
future with a higher sampling of the parameter space once new 
observations  clarify the kinematic nature of \tol \footnote{In
  Section \S \ref{sec:conclusions} we describe  in more detail what
  kind of observations could be performed in the near future to
  improve our understanding of \tol's kinematics.} . 
Considering the sparse sampling of parameter space and the results
from the random forest classifier, it is safer to consider that
the best values for $\sigma_{\rm cl}$, $v_{\infty {\rm cl}}$, $P_{\rm
  cl}$ are actually lower/upper/lower bounds, respectively.

@@

\tol\ shows one of the most atypical \lya\ spectra observed so far.
Its flux at the line's center is high compared to other LAEs at low
redshift and the broad, highly symmetrical peak is virtually absent from other
LAEs at low and high redshift
\citep{2012ApJ...751...29Y,LARS,Erb14,Trainor16}. 
Simple shell models
fail to reproduce such a spectrum as reported by \cite{2015A&A...578A...7V}.  
In the previous sections we show how these characteristics can be
explained by two different kinematic models: multiphase ISM and solid
body rotation.

@@

Following the results of \cite{2011ApJ...726..108T}, who made a
detailed analysis for all kind of elliptical galaxies including, we
estimate a value for the dynamical mass using the constraints for
thevelocity dispersion $\sigma$  in a spherical system localized in a
region of size $r$

\begin{equation}
M_{\rm dyn} = 3 \frac{\sigma ^{2}r}{G} = 3.48\times10^{9}
\left(\frac{\sigma}{100\ \mathrm{km\ s}^{-1}}\right)^2\left(\frac{r}{\mathrm{kpc}}\right)
M_{\odot}, 
\end{equation}
%
Assuming that the \lya\ emission is entirely powered by star formation 
we use the 3D half-light radius $r_s=2.25$ kpc as the typical size
for the HI region, in the multiphase model the clump velocity dispersion
$\sigma_{\rm{cl}}=$\sigmaclump corresponds to a dynamical mass of
$M_{\rm dyn}=2.31\pm0.04 \times 10^{9}$ $M_{\odot}$, which is ten
times the estimated baryonic mass in \tol.
Considering that the results for $\sigma_{\rm{cl}}$ are most probably
a lower bound, the results for the dynamical mass should also be
considered as a lower bound.

\cite{2011ApJ...726..108T} showed that  that such dynamical
mass can be explained if a dwarf galaxy is hosted by a dark matter halo of at
least $10^{11}$ M$_{\odot}$ in mass. 
This estimate is based on computing the integrated mass profile of a
spherical dark matter halo with a Navarro-Frenk-White profile with its
concentration following the median mass-concentration
relationship found in the Bolshoi simulation
\citep{2012MNRAS.423.3018P}.

These results would imply that \tol\ is part of the dE
class. 
However, there are two puzzles that are opened up by this hypothesis. 
First, dE galaxies are found either in clusters or groups of
galaxies; while \tol\ does not belong either to a group or a cluster
\citep{2001AJ....121..169F}. 
The second problem is that, unlike a dE, \tol\ hosts a bright and compact
startburst; imaging and spectroscopy studies suggest that the
startburst started less than 4 Myr ago, while the low surface
brightness regins are consistent with an age below one Gyr
\citep{2001AJ....121..169F}.

We suggest that new observational tests are needed to clarify the
kinematic nature of \tol\ and be sure about \tol's kinematic
structure. 
Integral field unit measurements resolving its spatial extent are up
to the task.  
\tol\ spans a region of $4$ arcseconds,
an instrument such as the Multi Unit Spectroscopic Explorer (MUSE)
\citep{2014Msngr.157...13B} with its nominal $0.2$ arcseconds spatial
sampling over a $1.0$ arcminute field in wide-field mode could provide
a coarse mapping of different ionization lines to infer a kinematic
map in the H$\alpha$ line, following the kind of work presented by
\citet{Herenz16} done with the Potsdam Multi-Aperture Spectrometer
(PMAS) \citep{PMAS} on nearby \lya\ emitting galaxies.

Another observational test to confirm the picture provided by the
multiphase model includes the measurement of the \lya\ ionizing
continuum escape fraction. 
This model model predicts that averaging over all sightlines
it should be around $0.5^{+1.0}_{-0.4}$\%, with the possibility of strong
variations depending on viewing angle, i.e. some sightlines can have
an escape fraction close to $100\%$, \citep{Gronke2016}.

@@

We prefer the multiphase model becasue it has kinematic
conditions similar to those in dwarf ellipticals, while the
rotational model produces rotational velocities to high for a dwarf
galaxy.

@@

All in all, the mere existence of a strong LAE galaxy with a broad,
highly symmetric line is interesting. 
\tol's line shape is different to others and seems to reveal an
unexpected kinematic structure.
A definitive confirmation of our findings has to be provided by new
observational tests with integral field unit spectroscopy. 
A confirmation of our results would support the multiphase model
as a tool to study the evolutionary link between star-forming and
quiescent stages of dwarf galaxy evolution.

>>>>

\begin{table}
\begin{center}
\begin{tabular}{lr}\hline
$\alpha$(2000)& 12h17min17.1s\\
$\delta$(2000)& -28d02m32s\\
$l$, $b$ (deg) & 294, 34\\
$m_V$ & 17.5\\
  M$_V$ & -17.6\\ 
Redshift & $0.026\pm0.001$ \\\hline
\end{tabular}
\end{center}
\caption{Basic observational characteristics of \tol\ 
  \citep{Thuan97}\label{obstable}} 
\end{table}

\begin{table*}
  \centering
\begin{tabular}{l|lrrl}
\hline
  Parameter  & Description & Fiducial value & Allowed range & Units \\ \hline\hline
$v_{\infty,\,{\rm cl}}$ & Radial cloud velocity & $100.0$ & [$0.0$, $800.0$] & $\,{\rm km\,s}^{-1}$ \\
$\sigma_{\rm {\rm cl}}$ & Random cloud motion &$40.0$ & [$5.0$, $100.0$] & $\,{\rm km\,s}^{-1}$ \\
$P_{\rm {\rm cl}}$ & Probability to be emitted in cloud & $0.35$ & [$0.0$, $1.0$] &  \\
$r_{\rm {\rm cl}}$ & Cloud radius & $100.0$ & [$30.0$, $200.0$] & $\,{\rm pc}$ \\
$H_{\rm em}$ & Emission scale radius & $1000.0$ & [$500.0$, $3.0\times 10^{3}$] & $\,{\rm pc}$ \\
$f_{\rm {\rm cl}}$ & Cloud covering factor & $3.5$ & [$0.8$, $8.0$] &  \\
$T_{\rm {\rm ICM}}$${}^{\dagger}$ & Temperature of ICM & $10^{6}$ & [$3.0\times 10^{5}$, $5.0\times 10^{7}$] & $\,{\rm K}$ \\
$n_{\rm HI,\,{\rm ICM}}$${}^{\dagger}$ & \HI number density in ICM & $5.0\times 10^{-8}$ & [$10^{-12}$, $10^{-6}$] & $\,{\rm cm}^{-3}$ \\
$\sigma_{\rm i}$ & Width of emission profile & $50.0$ & [$5.0$, $100.0$] & $\,{\rm km\,s}^{-1}$ \\
$T_{\rm {\rm cl}}$${}^{\dagger}$ & Temperature in clouds & $10^{4}$ & [$5.0\times 10^{3}$, $5.0\times 10^{4}$] & $\,{\rm K}$ \\
$\beta_{\rm cl}$ & Steepness of the radial velocity profile & $1.5$ & [$1.1$, $2.5$] &  \\
$\tilde\sigma_{\rm d, cl}$${}^{\dagger}$ & Dust content in clumps &
  $3.2\times10^{-22}$ & [$4.7\times 10^{-24}$, $1.6\times 10^{-21}$] &
  $\,\cm^{2}$ \\
$\zeta_d$${}^{\dagger}$ & Ratio of ICM to cloud dust abundance &
  $0.01$ & [$10^{-4}$, $0.1$] & \\
$n_{\rm HI,\,{\rm cl}}$${}^{\dagger}$ & \HI number density in
  clouds & $0.35$ & [$0.03$, $3.0$] & $\,{\rm cm}^{-3}$ \\
\hline
\end{tabular}
  \caption{Overview of the parameters in the multiphase model and its fiducial
    values. Variables marked with ${}^{\dagger}$ were drawn in
    log-space. Details of the implementation are in \citet{Gronke2016}.}
  \label{tab:models}
\end{table*}

@@

The idealized multiphase model consists of spherical, cold, dense
clumps of neutral hydrogen (and dust) embedded in a hot, ionized
medium \citep{Gronke2016}. 
The clumps also have a random and an outflowing velocity
component which totals the number of parameters describing the model
to be $14$.
We do not explore inflowing clumps given the slight line asymmetry
redwards to the line center (see the dots in Figure \ref{fig:results})
and thus set $v_{\infty,\,{\rm cl}}>0$.
The parameter description list is in Table \ref{tab:models}.

@@

We compare each resulting spectra to the observational results from
\tol\ after normalizing the observed and simulated spectra to have a 
flux integral of one.
We build a $\chi^2$ on the normalized flux measurements for each one
of the $2500$ models as

\begin{equation}
\chi^2 = \sum_{i} \frac{({f}_i - \hat{f}_i)^2}{\sigma_i^2}, 
\label{eq:chi2}
\end{equation}
%
where $i$ iterates over velocity bins, $f_{i}$ is the observed flux,
$\sigma_i$ is the observed flux uncertainty and $\hat{f}_i$ is the
model estimated flux.
As we do not have an analytic expression for $\hat{f}$; we use the
results of the MonteCarlo to build histograms that play the role of
$\hat{f}$.

We select for further analysis the best $1\%$ models according to the
lowest $\chi^2$ values.
We note that the difference between the lowest and highest $\chi^2$ values in
those $25$ models is close to $\Delta\chi^2 = 3000$, the lowest
$\chi^2$ being close to $\chi^2_{min}=1200$.

Using the total number of degrees of freedom, $d.o.f.=104$ we divide
the results in two classes: low $\chi^2/d.o.f.<35$ and high
$\chi^2/d.o.f.35>$. 
We apply a random forest classification algorithm to find the
more relevant parameters in splitting the results into these two
classes. 
The algorithm uses $500$ trees for the classification and a
maximum of $3$ depth levels. 
To check for stability we repeat the computation $10$ times by
randomly subsampling the input data to use $80\%$ of the data as
the training set.

@@

We use an analytical approximation that captures the most important
effects of rotation onto the \lya\ line. 
We defer the reader to \citet{GaravitoCamargo2014} for complete
details on the explicit form of this approximation.
To fully explore the
parameter space using a Markov Chain Monte Carlo (MCMC) calculation with the
\texttt{emcee} Python library \citep{2013PASP..125..306F}. \texttt{emcee} 
is an open source optimized implementation of the affine-invariant 
MCMC sampler \citep{goodman2010ensemble}. 
The algorithm creates a number of walkers that,
during a sufficient number of steps, generate parameters' combinations
for a specific model.
For each timestep, the code calculates the likelihood of the
combination with respect to the observational data.
The walkers explore the parameter space sampling the Gaussian likelihood
function built as $\propto \exp(-\chi^2/2)$, where the $\chi^2$ follows
the definition in Equation \ref{eq:chi2}. 
We do not have a closed analytic expresion for $\hat{f}$, we compute it
by numerical integration of the analytical approximations found in
\citet{GaravitoCamargo2014}.

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.95\textwidth]{tree_result.pdf}
\caption{Classification tree example. 
The aim is to find the parameters that separate two
classes: low $\chi^2/d.o.f. < 35$ and high $\chi^2/d.o.f>35$. 
Each box describes the condition over the parameter of interest, the
level of sample impurity, the total number of samples and the value of the
number of samples in each class.  
In this example we randomly sample $80\%$ of the full data set of models to
start with $28$ models in the first class and
$1962$ models in the second class; the best way to increase the
probability to find a result with low $\chi^2/d.o.f.$ ($13$ models,
fourth bottom box, from left to the right)
is having the clump radial velocity, $v_{\infty,{\rm cl}}<157.0$ \kms;
the clump velocity dipersion, $\sigma_{{\rm cl}}>55.6$ \kms, and the
probability to have a \lya\ photon emitted in a clump, $P_{\rm cl}>0.683$.
The final classification is not perfect, showing that all other
parameters are also important but these three are the most relevant.  
\label{fig:tree}}
\end{center}
\end{figure*}

\begin{figure*}
\begin{center}
  \includegraphics[width=0.6\textwidth]{vinf_cl.pdf}
  \includegraphics[width=0.6\textwidth]{P_cl.pdf}
  \includegraphics[width=0.6\textwidth]{sigma_cl.pdf}
\caption{Results from the multiphase  model.
  We only show results for the three parameters with a significant
  statistical difference between the models with the lowest $\chi^2/d.o.f.$
  values and its prior distribution. 
  These three parameters are the clump radial velocity at infinity 
  $v_{\infty, \rm{cl}}$; the probability that  the \lya\ photons were
  emitted in the clumps, $P_{\rm cl}$; the clump velocity dispersion,
  $\sigma_{\rm cl}$.
  The left column corresponds to the parameter's integrated distributions for
  models with the lowest $\chi^2/d.o.f.$ values (dotted line) compared against the
  parameter's prior integrated distributions (continuous line).
  The right column shows a scatter plot of $\chi^2/d.o.f.$
  and its corresponding physical parameters.
  The clump kinematic state is the key ingredient to
  reproduce \tol's \lya\ line morphology.
  \label{multiphaseresults}
}  
\end{center}
\end{figure*}

@@

Figure \ref{fig:tree} shows as an illustration the results for a
single classification tree.  
The tree starts with $28$ and $1962$ models in the low and high
$\chi^2/d.o.f.$ classes, respectively. 
We find that the best classification
yields $13$ and $44$ models in the low and high $\chi^2/d.o.f.$
classes, respectively, after selecting for $v_{\infty,{\rm cl}}<157.0$ \kms,
$\sigma_{{\rm cl}}>55.6$ \kms and $P_{\rm cl}>0.683$. 
The split in two classes is not perfect. 
This means that the 3 parameters in the
model are the most influential in finding models with low
$\chi^2/d.o.f.$, but that some combinations of the other 11 parameters
are also relevant to find a good fit.

@@

The best models are shown in Figure \ref{multiphaseresults}.
Left column shows the difference between the integrated distributions
of the full sample (2500 input models) and the models with the lowest
$\chi^2/d.o.f.$. 
The right column shows the actual $\chi^2/d.o.f.$ 
and its corresponding parameter value. 
Under these conditions we find $\sigma_{\rm cl}=$\sigmaclump,
$v_{\infty {\rm, cl}}=$\inftyclump\ and $P_{\rm cl}=$\probaclump.

@@

Having constrained only 3 parameters, one migh wonder why the other 11
parameters do not seem to matter. 
However, this view is misleading. 
Even if for clumply models the line profile is most sensitive to only
a few parameters \citep{Gronke2016}, there are the rest of parameters
which affect the line profile at a level that cannot be neglected,
i.e. we cannot randomly pick 11 random, reasonable values for these
parameters, and expect to fit the line profile while only varying the
other 3, as the results for the classification tree example in Figure
\ref{fig:tree} shows.

We cannot discard that another region of parameter space
could also work.
It might be interesting to explore in the
future with a higher sampling of the parameter space once new 
observations  clarify the kinematic nature of \tol \footnote{In
  Section \S \ref{sec:conclusions} we describe  in more detail what
  kind of observations could be performed in the near future to
  improve our understanding of \tol's kinematics.} . 
Furthermore, considering the sparse sampling of parameter space and the results
from the random forest classifier, it is safer to consider that
the best values for $\sigma_{\rm cl}$, $v_{\infty {\rm cl}}$, $P_{\rm
  cl}$ are actually lower/upper/lower bounds, respectively.

@@

\tol\ presents one of the most atypical \lya\ spectra observed so far.
Its flux at the line's center is high compared to other LAEs at low
redshift and the broad, highly symmetrical peak is virtually absent from other
LAEs at low and high redshift
\citep{2012ApJ...751...29Y,LARS,Erb14,Trainor16}. 
Simple shell models
fail to reproduce such a spectrum as reported by \cite{2015A&A...578A...7V}.  
In the previous sections we show how these characteristics can be
explained by two different kinematic models: multiphase ISM and solid
body rotation.

@@

Following the results of \cite{2011ApJ...726..108T}, who made a
detailed analysis for all kind of elliptical galaxies including dE galaxies, we
estimate a value for the dynamical mass using the constraints for
thevelocity dispersion, $\sigma$,  in a spherical system localized in a
region of size $r$

\begin{equation}
M_{\rm dyn} = 3 \frac{\sigma ^{2}r}{G} = 3.48\times10^{9}
\left(\frac{\sigma}{100\ \mathrm{km\ s}^{-1}}\right)^2\left(\frac{r}{\mathrm{kpc}}\right)
M_{\odot}, 
\end{equation}
%
Assuming that the \lya\ emission is entirely powered by star formation 
we use the 3D half-light radius $r_s=2.25$ kpc as the typical size
for the HI region, in the multiphase model the clump velocity dispersion
$\sigma_{\rm{cl}}=$\sigmaclump thus corresponds to a dynamical mass of
$M_{\rm dyn}=2.31\pm0.04 \times 10^{9}$ $M_{\odot}$, which is ten
times the estimated baryonic mass in \tol.
Considering that the results for $\sigma_{\rm{cl}}$ are most probably
a lower bound, the results for the dynamical mass should also be
considered as a lower bound.

\cite{2011ApJ...726..108T} showed that  that such dynamical
mass can be explained if a dE is hosted by a dark matter halo of at
least $10^{11}$ M$_{\odot}$ in mass. 
This estimate is based on computing the integrated mass profile of a
spherical dark matter halo with a Navarro-Frenk-White profile with its
concentration following the median mass-concentration
relationship found in the Bolshoi simulation
\citep{2012MNRAS.423.3018P}.

These results would imply that \tol\ is part of the dE
class. 
However, there are two puzzles that are opened up by this hypothesis. 
First, dE galaxies are found either in clusters or groups of
galaxies; while \tol\ does not belong either to a group or a cluster
\citep{2001AJ....121..169F}. 
The second issue is that, unlike a dE, \tol\ hosts a bright and compact
startburst; imaging and spectroscopy studies suggest that the
startburst started less than 4 Myr ago, while the low surface
brightness regins are consistent with an age below one Gyr
\citep{2001AJ....121..169F}.

We suggest that new observational tests are needed to clarify the
kinematic nature of \tol\.
Integral field unit measurements resolving its spatial extent are up
to the task.  
\tol\ spans a region of $4$ arcseconds,
an instrument such as the Multi Unit Spectroscopic Explorer (MUSE)
\citep{2014Msngr.157...13B} with its nominal $0.2$ arcseconds spatial
sampling over a $1.0$ arcminute field in wide-field mode could provide
a coarse mapping of different ionization lines to infer a kinematic
map in the H$\alpha$ line, following the kind of work presented by
\citet{Herenz16} done with the Potsdam Multi-Aperture Spectrometer
(PMAS) \citep{PMAS} on nearby \lya\ emitting galaxies.

Another observational hint to clarify \tol's state could be
the measurement of the \lya\ ionizing continuum escape fraction. 
The multiphase model predicts that averaging over all sightlines
it should be around $0.5^{+1.0}_{-0.4}$\%, with the possibility of strong
variations depending on viewing angle, i.e. some sightlines can have
an escape fraction close to $100\%$, \citep{Gronke2016}.

@@

In this particular case, we prefer the multiphase model becasue it has kinematic
conditions similar to those in dwarf ellipticals, while the
rotational model produces rotational velocities too high for a dwarf
galaxy.

@@

All in all, the mere existence of a strong LAE galaxy with a broad,
highly symmetric line is interesting. 
\tol's line shape is different to others and seems to reveal an
unexpected kinematic structure.
A confirmation of our results by new observations would support the multiphase model
as an element to be included in the study of primordial \lya\ emitting
galaxies.
